DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/comparison.tex
Minor changes to comparison section

The Intel UP board and Jetson TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

>>>>

The Intel UP board and Jetson TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 30 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. However, we found that the TX2's GPU may not have the capacity
necessary to support multiple models running simultaneously. 
It was unable to co-schedule 4 DNN models due to insufficient memory, 
hence why there is no data entry for the 4Nx1C test. In our experiements,
we found that the TX2's GPU could run at most 3 models concurrently, as 
any more would result in one of the models being terminated.
